Papers

### 2023-09-23 quarto/index.qmd
update

**Aston Zhang** is a research scientist at Meta Generative AI, designing and training large models.
Previously, he studied language models and multimodality for AI at Amazon Web Services AI Research.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.

@@

* Z. Zhang and **A. Zhang**<br>
<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
*"Perform a task on smart phones? Train an agent using screenshots."*
In *arXiv*, 2023<br>
<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

>>>>

**Aston Zhang** is a research scientist at Meta Generative AI, building large language models.
Previously, he was a scientist at Amazon Web Services AI Research.
He received an <a href="https://iclr-conf.medium.com/announcing-iclr-2021-outstanding-paper-awards-9ae0514734ab" target="_blank">ICLR Outstanding Paper Award</a>,
an ACM Ubicomp Distinguished Paper Award, and an ACM SenSys Best Paper Award Nomination.
His <a href="https://github.com/d2l-ai" target="_blank">open-source</a> textbook,
<a href="https://d2l.ai" target="_blank">Dive into Deep Learning</a>,
has been <a href="https://d2l.ai/_images/map.png" target="_blank">adopted worldwide</a>.
He obtained his Ph.D. in Computer Science from University of Illinois at Urbana-Champaign.

@@

* Z. Zhang and **A. Zhang**<br>
<a href="https://arxiv.org/abs/2309.11436" target="_blank">You Only Look at Screens: Multimodal Chain-of-Action Agents</a><br>
*"Perform a task on smart phones? Train an agent using screenshots."*
In *arXiv*, 2023<br>
<a href="https://twitter.com/astonzhangAZ/status/1705235421280797111" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/cooelf/Auto-UI" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
